### 2023-01-20 my_paper/FinalDraft.tex
edits

\begin{align} \label{eq:iden}
Y_{it} &= \beta_{1} HW_{i} +  \beta_{2} WH_{i} + \beta_{3} HH_{i} +\\
& \beta_{4} WH_{i} \cdot Hispanic_{i} + \beta_{5} HW_{i}\cdot Hispanic_{i} +  \beta_{6} HH_{i} \cdot Hispanic_{i}+ \nonumber \\
&X_{it}^{\prime} + \gamma_{t}+\phi_{it} \nonumber
\end{align}

>>>>

\begin{align} \label{eq:iden}
Y_{it} &= \beta_{1} HW_{i} +  \beta_{2} WH_{i} + \beta_{3} HH_{i} +\\
& \beta_{4} WH_{i} \cdot Hispanic_{i} + \beta_{5} HW_{i}\cdot Hispanic_{i} +  \beta_{6} HH_{i} \cdot Hispanic_{i}+ \nonumber \\
&X_{it} \pi + \gamma_{t}+\phi_{it} \nonumber
\end{align}
